flash alpha version

### 2017-06-30 analysis/flash_alpha_versino.Rmd
Files commited by wflow_commit.

---
title: "objective function with the penalty term"
author: "wei"
date: YYYY-MM-DD
output: html_document
---

@@

In this case, we would like to try the objective function with penalty term.

I would like to modify the flash code in this document.

```{r,echo=FALSE}
source("../code/flash_reg_170620.R")
```

@@

### check the new obj function

we check that the new objective function with penalty term does monotonically increase.

@@

```{r}
objcheck_1(K=1,N = 20, P=30, SF = 0.5, SL = 0.6, signal = 1,noise = 1)
```

```{r}
objcheck_1(K=1,N = 200, P=300, SF = 0.8, SL = 0.6, signal = 1,noise = 1)
```

```{r}
objcheck_1(K=1,N = 200, P=300, SF = 0.9, SL = 0.8, signal = 1,noise = 1)
```

```{r}
objcheck_1(K=1,N = 200, P=300, SF = 0.5, SL = 0.9, signal = 1,noise = 3)
```

```{r}
objcheck_1(K=1,N = 100, P=200, SF = 0.8, SL = 0.9, signal = 1,noise = 3)
```

we can see that the old version of code without penalty doesn't have monotonically increasing objective function, but the new version code with penalty term does.

*now we have two methods (fdr, shrink), and both of them have monotonically increasing corresponding objective function in each case.*

## try the same problem: rank 0 vs rank 1 with  fdr method.

```{r,echo = FALSE}

rank0check = function(K=1,N = 100, P=200, SF = 0.5, SL = 0.5, signal = 0,noise = 1, mtype = "fdr"){
  data = sim_K(K,N, P, SF , SL , signal ,noise )
  Y = data$Y
  E = data$Error
  if(mtype == "fdr"){
    g1 = flash(Y,objtype = "l")
  }else{
    g1 = flash(Y,objtype = "l",ash_para = list(method = "shrink"))
  }

  RMSE = sqrt(mean((Y - g1$l %*% t(g1$f) -E)^2)) 
  RMSE0 = sqrt(mean((Y  -E)^2)) 
  obj_val = g1$obj_val
  # to get the rank zero objective value
  sigmae2_v0 = Y^2
  fit_g0 = list(pi=c(1,0,0),sd = c(0,0.1,1))
  mat0 = list(comp_postmean = matrix(0,ncol= N,nrow = 3),
              comp_postmean2 = matrix(0,ncol= N,nrow = 3),
              comp_postprob = matrix(0,ncol= N,nrow = 3))
  mat0$comp_postprob[1,] = 1
  par_l0 = list(g = fit_g0, mat = mat0)
  fit_g0 = list(pi=c(1,0,0),sd = c(0,0.1,1))
  mat0 = list(comp_postmean = matrix(0,ncol= P,nrow = 3),
              comp_postmean2 = matrix(0,ncol= P,nrow = 3),
              comp_postprob = matrix(0,ncol= P,nrow = 3))
  mat0$comp_postprob[1,] = 1
  par_f0 = list(g = fit_g0, mat = mat0)
  obj0 = obj(N,P,sigmae2_v0,sigmae2 = mean(sigmae2_v0),par_f0,par_l0,objtype = "lowerbound_lik",ash_para = list(method = NULL))

  return(list(rmse = RMSE,rmse0 = RMSE0,obj_val = obj_val,obj_0 = obj0))
}

sim_rank0 = function(K=1,N = 100, P=200, SF = 0.5, SL = 0.5, signal = 0,noise = 1,mtype = "fdr"){
  T = 200
  RMSE = rep(NA,T)
  diff_obj = rep(NA,T)
  for(t in 1:T){
    g0 = rank0check(K = 1,N, P, SF, SL , signal,noise,mtype = mtype)
    RMSE[t] = g0$rmse
    diff_obj[t] = (g0$obj_val - g0$obj_0)
  }
  par(mfrow = c(2, 2))
  par(cex = 0.6)
  par(mar = c(3, 3, 0.8, 0.8), oma = c(1, 1, 1, 1))
  boxplot(RMSE,main = "RMSE")
  hist(diff_obj, breaks = 50,main = "sign of difference of obj value")
  hist(RMSE,breaks = 50,main = "RMSE")
  plot(diff_obj,RMSE, main = "sign of obj diff vs RMSE")
  return(c(sum(diff_obj == 0),sum(diff_obj>0),sum(diff_obj<0))/T)
}

```

#### case 1: rank 0

we compare the old code with our new code, we can see that most of the cases a

*shrink method without penalty*

```{r}
set.seed(99)
sim_rank0(K=1,N = 100, P=200, SF = 0.5, SL = 0.5, signal = 0,noise = 1,mtype = "shrink")
```

*fdr method with penalty*

```{r}
set.seed(99)
sim_rank0(K=1,N = 100, P=200, SF = 0.5, SL = 0.5, signal = 0,noise = 1)
```

we can see the improvement that the proportion of P(estimated structure better than rank 0 structure) is much larger.

#### case 2: rank 1, very sparse with large noise

*shrink method without penalty*

```{r}
set.seed(99)
sim_rank0(K=1,N = 100, P=200, SF = 0.8, SL = 0.8, signal = 1,noise = 2,mtype = "shrink")
```

*fdr method with penalty*

```{r}
set.seed(99)
sim_rank0(K=1,N = 100, P=200, SF = 0.8, SL = 0.8, signal = 1,noise = 2)
```

we can see that the results are improved since the proportion of P(estimated structure better than rank 0 structure) is much larger.

In this case we can see that the RMSE is negative correlated with the objective function value. So it is make sense that we return $g_l = 0, g_f = 0$ if the $LB(estimated) < LB(g_l=0,g_f = 0)$.

>>>>

---
title: "flash alpha version"
author: "Wei"
date: YYYY-MM-DD
output: html_document
---

@@

```{r}
source("../code/flash_reg_170620.R")
```

@@

@@

```{r}
# test the obj0
K=1;N = 200; P=300; SF = 0.5; SL = 0.6; signal = 0.1; noise = 1
data = sim_K(K,N, P, SF , SL , signal ,noise )
Y = data$Y
E = data$Error
g1 = flash(Y,objtype = "l")
g2 = flash(Y,objtype = "m")

sigmae2_v0 = Y^2
  fit_g0 = list(pi=c(1,0,0),sd = c(0,0.1,1))
  mat0 = list(comp_postmean = matrix(0,ncol= N,nrow = 3),
              comp_postmean2 = matrix(0,ncol= N,nrow = 3),
              comp_postprob = matrix(0,ncol= N,nrow = 3))
  mat0$comp_postprob[1,] = 1
  par_l0 = list(g = fit_g0, mat = mat0)
  fit_g0 = list(pi=c(1,0,0),sd = c(0,0.1,1))
  mat0 = list(comp_postmean = matrix(0,ncol= P,nrow = 3),
              comp_postmean2 = matrix(0,ncol= P,nrow = 3),
              comp_postprob = matrix(0,ncol= P,nrow = 3))
  mat0$comp_postprob[1,] = 1
  par_f0 = list(g = fit_g0, mat = mat0)
  obj0 = obj(N,P,sigmae2_v0,sigmae2 = mean(sigmae2_v0),par_f0,par_l0,objtype = "lowerbound_lik",ash_para = list(method = NULL))
  Fval(par_f0$mat, par_f0$g,ash_para=list(method = NULL))
```
